An Imaging Search for Post-Main-Sequence Planets of Sirius B

### 2021-11-19 paper/paper.tex
add back pagenumbers
updat elanguage

Exoplanets are faint enough that only a few photons per second reach the detector. The host stars are many orders of magnitude brighter than the thermal emission of giant planets ($\sim10^{\text{-}8}$) and have close angular separations, which means planets are easily washed out by the stellar diffraction pattern \citep{traubDirectImagingExoplanets2010}. In addition, atmospheric seeing and instrumental aberrations greatly reduce the sensitivity to exoplanets due to the manifestation of quasi-random perturbations of the instrumental point-spread function (speckles, see \citealp{guyonExtremeAdaptiveOptics2018}). Adaptive optics (AO) corrects a large percentage of the effects of speckles but has decreasing efficacy for dim targets due to the photon-limited nature of modern AO instrumentation. AO is also paramount for enabling coronagraphy, which attenuates on-axis starlight while transmitting off-axis signal, up to some inner working angle.

@@

% White dwarfs are interesting targets for direct imaging- they are three to four orders of magnitude fainter than their MS progenitors, reducing the contrast necessary to detect a companion. The lack of spectral features in white dwarfs \citep{schatzmanTheorieDebitEnergie1945} makes them difficult targets for the radial velocity technique. The small stellar radii of white dwarfs lowers the transit probability significantly, although detections of substellar companions around white dwarfs have been made \citep[e.g.,][]{vanderburgGiantPlanetCandidate2020}. The intrinsic faintness of white dwarfs proves challenging due to the high signal-to-noise ratio (S/N) required by AO. This is exacerbated on ground-based telescopes which require extreme AO to counteract the effects of atmospheric seeing. This constrains potential companion searches to relatively bright targets ($m^R\lesssim$ 13). Implicitly, this also limits searches to nearby white dwarfs ($d\sim$\qty{25}{\parsec}, \citealp{holberg25ParsecLocal2016}), which is beneficial for imaging because the limited inner working angle of the instrumentation will project to closer separations around closer stars.

>>>>

Exoplanets are faint enough that only a few photons per second reach the detector. Host stars are typically many orders of magnitude brighter than the thermal emission of giant planets ($\sim10^{\text{-}8}$), and planets have very small angular separations from their hosts, which makes it difficult to disentangle the planet-light from the stellar diffraction pattern \citep{traubDirectImagingExoplanets2010}. In addition, atmospheric seeing and instrumental aberrations greatly reduce the sensitivity to exoplanets due to the manifestation of quasi-random perturbations of the instrumental point-spread function (speckles, see \citealp{guyonExtremeAdaptiveOptics2018}). Adaptive optics (AO) corrects a large percentage of the effects of speckles but has decreasing efficacy for dim targets due to the photon-limited nature of modern AO instrumentation. AO is also paramount for enabling coronagraphy, which attenuates on-axis starlight while transmitting off-axis signal, up to some inner working angle.

@@

% White dwarfs are interesting targets for direct imaging- they are three to four orders of magnitude fainter than their MS progenitors, reducing the contrast necessary to detect a companion. The lack of spectral features in white dwarfs \citep{schatzmanTheorieDebitEnergie1945} makes them difficult targets for the radial velocity technique. The small stellar radii of white dwarfs lowers the transit probability significantly, although detections of substellar companions around white dwarfs have been made \citep[e.g.,][]{vanderburgGiantPlanetCandidate2020}. The intrinsic faintness of white dwarfs proves challenging due to the high signal-to-noise ratio (S/N) required by AO. This is exacerbated on ground-based telescopes which require extreme AO to counteract the effects of atmospheric seeing. This constrains potential companion searches to relatively bright targets ($m^R\lesssim$ 13). Implicitly, this also limits searches to nearby white dwarfs ($d\sim$\qty{25}{\parsec}, \citealp{holberg25ParsecLocal2016}), which is beneficial for imaging because the limited inner working angle of the instrumentation will project to closer separations around closer stars.
\pagebreak
